Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-22 paper/structureScene.tex
title of section III = "Scattering representations"

\section{Scattering transforms}
Scattering transforms are translation-invariant representations of audio signals which cascade an auditory filterbank and a modulation filterbank, interspersed with complex modulus nonlinearities.
Depending upon the chosen architecture, the modulation filterbank may either be performed solely over the time variable or on both time and frequency.
In this section, we present both the temporal scattering transform and the time-frequency scattering transform.

>>>>

\section{Scattering representations}
Scattering transforms are translation-invariant representations of audio signals which cascade an auditory filterbank and a modulation filterbank, interspersed with complex modulus nonlinearities.
Depending upon the chosen architecture, the modulation filterbank may either be performed solely over the time variable or on both time and frequency.
In this section, we present both the temporal scattering transform and the time-frequency scattering transform.
